Paper 1: Vitis

### 2018-02-06 Paper-1-Vitis.Rmd
Commit from RStudio

```{r}
ac_all <- read_excel("R_DilP_Vitis_all_added.xlsx", sheet = "acerifolia.all.90")
str(ac_all)
ac_all$year <- as.factor(ac_all$year)
ac_all$tooth.area <- as.numeric(ac_all$tooth.area)
ac_all$tooth.area.perimeter <- as.numeric(ac_all$tooth.area.perimeter)
ac_all$tooth.area.int.perimeter <- as.numeric(ac_all$tooth.area.int.perimeter)
ac_all$average.tooth.area <- as.numeric(ac_all$average.tooth.area)
ac_all$tooth.area.blade.area <- as.numeric(ac_all$tooth.area.blade.area)
t.test(ac_all$total.teeth~ac_all$year, var.equal = TRUE)
t.test(ac_all$feret.diameter.ratio~ac_all$year, var.equal = TRUE)
t.test(ac_all$feret.diameter.ratio~ac_all$year, var.equal = TRUE)
t.test(ac_all$tooth.area.perimeter~ac_all$year, var.equal = TRUE)
t.test(ac_all$tooth.area.int.perimeter~ac_all$year, var.equal = TRUE)
t.test(ac_all$average.tooth.area~ac_all$year, var.equal = TRUE)
t.test(ac_all$tooth.area.blade.area~ac_all$year, var.equal = TRUE)
t.test(ac_all$teeth.perimeter~ac_all$year, var.equal = TRUE)
t.test(ac_all$teeth.int.perimeter~ac_all$year, var.equal = TRUE)
t.test(ac_all$perimeter.area~ac_all$year, var.equal = TRUE)
t.test(ac_all$perimeter.ratio~ac_all$year, var.equal = TRUE)
t.test(ac_all$compactness~ac_all$year, var.equal = TRUE)
t.test(ac_all$shape.factor~ac_all$year, var.equal = TRUE)
t.test(ac_all$teeth.blade.area~ac_all$year, var.equal = TRUE)
```
Only one variable showed a statistically significant different changes between growing seasons: tooth area to blade area (TABA).

>>>>

```{r}
ac_all <- read_excel("R_DilP_Vitis_all_added.xlsx", sheet = "acerifolia.all.90")
str(ac_all)
ac_all$year <- as.factor(ac_all$year)
ac_all$tooth.area <- as.numeric(ac_all$tooth.area)
ac_all$tooth.area.perimeter <- as.numeric(ac_all$tooth.area.perimeter)
ac_all$tooth.area.int.perimeter <- as.numeric(ac_all$tooth.area.int.perimeter)
ac_all$average.tooth.area <- as.numeric(ac_all$average.tooth.area)
ac_all$tooth.area.blade.area <- as.numeric(ac_all$tooth.area.blade.area)
skim(ac_all)
t.test(ac_all$total.teeth~ac_all$year, var.equal = TRUE)
t.test(ac_all$feret.diameter.ratio~ac_all$year, var.equal = TRUE)
t.test(ac_all$tooth.area.perimeter~ac_all$year, var.equal = TRUE)
t.test(ac_all$tooth.area.int.perimeter~ac_all$year, var.equal = TRUE)
t.test(ac_all$average.tooth.area~ac_all$year, var.equal = TRUE)
t.test(ac_all$tooth.area.blade.area~ac_all$year, var.equal = TRUE)
t.test(ac_all$teeth.perimeter~ac_all$year, var.equal = TRUE)
t.test(ac_all$teeth.int.perimeter~ac_all$year, var.equal = TRUE)
t.test(ac_all$perimeter.area~ac_all$year, var.equal = TRUE)
t.test(ac_all$perimeter.ratio~ac_all$year, var.equal = TRUE)
t.test(ac_all$compactness~ac_all$year, var.equal = TRUE)
t.test(ac_all$shape.factor~ac_all$year, var.equal = TRUE)
t.test(ac_all$teeth.blade.area~ac_all$year, var.equal = TRUE)
```
Only one variable showed a statistically significant changes between growing seasons: tooth area to blade area (TABA).

We next tested each of the variables for *Vitis aestivalis*.

```{r}
av_all <- read_excel("R_DilP_Vitis_all_added.xlsx", sheet = "aestivalis.all.90")
av_all$year <- as.factor(av_all$year)
av_all$petiole.width.area <- as.numeric(av_all$petiole.width.area)
av_all$petiole.area <- as.numeric(av_all$petiole.area)
av_all$major.feret <- as.numeric(av_all$major.feret)
av_all$tooth.area <- as.numeric(av_all$tooth.area)
av_all$feret.diameter.ratio <- as.numeric(av_all$feret.diameter.ratio)
av_all$tooth.area.perimeter <- as.numeric(av_all$tooth.area.perimeter)
av_all$tooth.area.int.perimeter <- as.numeric(av_all$tooth.area.int.perimeter)
av_all$average.tooth.area <- as.numeric(av_all$average.tooth.area)
av_all$tooth.area.blade.area <- as.numeric(av_all$tooth.area.blade.area)
str(av_all)
skim(av_all)
t.test(av_all$total.teeth~av_all$year, var.equal = TRUE)
t.test(av_all$feret.diameter.ratio~av_all$year, var.equal = TRUE)
t.test(av_all$tooth.area.perimeter~av_all$year, var.equal = TRUE)
t.test(av_all$tooth.area.int.perimeter~av_all$year, var.equal = TRUE)
t.test(av_all$average.tooth.area~av_all$year, var.equal = TRUE)
t.test(av_all$tooth.area.blade.area~av_all$year, var.equal = TRUE)
t.test(av_all$teeth.perimeter~av_all$year, var.equal = TRUE)
t.test(av_all$teeth.int.perimeter~av_all$year, var.equal = TRUE)
t.test(av_all$perimeter.area~av_all$year, var.equal = TRUE)
t.test(av_all$perimeter.ratio~av_all$year, var.equal = TRUE)
t.test(av_all$compactness~av_all$year, var.equal = TRUE)
t.test(av_all$shape.factor~av_all$year, var.equal = TRUE)
t.test(av_all$teeth.blade.area~av_all$year, var.equal = TRUE)
```
Four variables showed statistically significant changes between growing seasons: total teeth (TT), tooth area to blade area (TABA), compactness (CP), shape factor (SF).

We next tested each of the variables for *Vitis amurensis*.

```{r}
am_all <- read_excel("R_DilP_Vitis_all_added.xlsx", sheet = "amurensis.all.90")
am_all$year <- as.factor(am_all$year)
am_all$petiole.width <- as.numeric(am_all$petiole.width)
am_all$petiole.width.area <- as.numeric(am_all$petiole.width.area)
am_all$petiole.area <- as.numeric(am_all$petiole.area)
am_all$blade.area <- as.numeric(am_all$blade.area)
am_all$feret.diameter <- as.numeric(am_all$feret.diameter)
am_all$major.feret <- as.numeric(am_all$major.feret)
am_all$leaf.area <- as.numeric(am_all$leaf.area)
am_all$perimeter <- as.numeric(am_all$perimeter)
am_all$internal.perimeter <- as.numeric(am_all$internal.perimeter)
am_all$feret.diameter.ratio <- as.numeric(am_all$feret.diameter.ratio)
am_all$tooth.area.perimeter <- as.numeric(am_all$tooth.area.perimeter)
am_all$tooth.area.int.perimeter <- as.numeric(am_all$tooth.area.int.perimeter)
am_all$tooth.area.blade.area <- as.numeric(am_all$tooth.area.blade.area)
am_all$teeth.perimeter <- as.numeric(am_all$teeth.perimeter)
am_all$teeth.int.perimeter <- as.numeric(am_all$teeth.int.perimeter)
am_all$perimeter.area <- as.numeric(am_all$perimeter.area)
am_all$perimeter.ratio <- as.numeric(am_all$perimeter.ratio)
am_all$compactness <- as.numeric(am_all$compactness)
am_all$shape.factor <- as.numeric(am_all$shape.factor)
am_all$teeth.blade.area <- as.numeric(am_all$teeth.blade.area)
str(am_all)
skim(am_all)
t.test(am_all$total.teeth~am_all$year, var.equal = TRUE)
t.test(am_all$feret.diameter.ratio~am_all$year, var.equal = TRUE)
t.test(am_all$tooth.area.perimeter~am_all$year, var.equal = TRUE)
t.test(am_all$tooth.area.int.perimeter~am_all$year, var.equal = TRUE)
t.test(am_all$average.tooth.area~am_all$year, var.equal = TRUE)
t.test(am_all$tooth.area.blade.area~am_all$year, var.equal = TRUE)
t.test(am_all$teeth.perimeter~am_all$year, var.equal = TRUE)
t.test(am_all$teeth.int.perimeter~am_all$year, var.equal = TRUE)
t.test(am_all$perimeter.area~am_all$year, var.equal = TRUE)
t.test(am_all$perimeter.ratio~am_all$year, var.equal = TRUE)
t.test(am_all$compactness~am_all$year, var.equal = TRUE)
t.test(am_all$shape.factor~am_all$year, var.equal = TRUE)
t.test(am_all$teeth.blade.area~am_all$year, var.equal = TRUE)
```

Many variables showed statistically significant changes between growing seasons: total teeth (TT), tooth area to perimeter (TAP), tooth area to internal perimeter (TAIP), average tooth area (ATA), *total teeth to perimeter (TP)*, *perimeter to area (PA)*, perimeter to ratio (PR), *compactness (CP)*, and shape factor (SF).

We finally tested each of the variables for *Vitis riparia*.

```{r}
r_all <- read_excel("R_DilP_Vitis_all_added.xlsx", sheet = "riparia.all.90")
r_all$year <- as.factor(r_all$year)
r_all$petiole.width <- as.numeric(r_all$petiole.width)
r_all$petiole.width.area <- as.numeric(r_all$petiole.width.area)
r_all$petiole.area <- as.numeric(r_all$petiole.area)
r_all$internal.perimeter <- as.numeric(r_all$internal.perimeter)
r_all$tooth.area <- as.numeric(r_all$tooth.area)
r_all$tooth.area.perimeter <- as.numeric(r_all$tooth.area.perimeter)
r_all$tooth.area.int.perimeter <- as.numeric(r_all$tooth.area.int.perimeter)
r_all$average.tooth.area <- as.numeric(r_all$average.tooth.area)
r_all$tooth.area.blade.area <- as.numeric(r_all$tooth.area.blade.area)
r_all$teeth.int.perimeter <- as.numeric(r_all$teeth.int.perimeter)
r_all$perimeter.ratio <- as.numeric(r_all$perimeter.ratio)
r_all$teeth.blade.area <- as.numeric(r_all$teeth.blade.area)
str(r_all)
skim(r_all)
t.test(r_all$total.teeth~r_all$year, var.equal = TRUE)
t.test(r_all$feret.diameter.ratio~r_all$year, var.equal = TRUE)
t.test(r_all$tooth.area.perimeter~r_all$year, var.equal = TRUE)
t.test(r_all$tooth.area.int.perimeter~r_all$year, var.equal = TRUE)
t.test(r_all$average.tooth.area~r_all$year, var.equal = TRUE)
t.test(r_all$tooth.area.blade.area~r_all$year, var.equal = TRUE)
t.test(r_all$teeth.perimeter~r_all$year, var.equal = TRUE)
t.test(r_all$teeth.int.perimeter~r_all$year, var.equal = TRUE)
t.test(r_all$perimeter.area~r_all$year, var.equal = TRUE)
t.test(r_all$perimeter.ratio~r_all$year, var.equal = TRUE)
t.test(r_all$compactness~r_all$year, var.equal = TRUE)
t.test(r_all$shape.factor~r_all$year, var.equal = TRUE)
t.test(r_all$teeth.blade.area~r_all$year, var.equal = TRUE)
```

Many variables showed statistically significant changes between growing seasons: tooth area to internal perimeter (TAIP), tooth area to blade area (TABA), total teeth to perimeter (TP), total teeth to internal perimeter (TIP), perimeter ratio (PR), compactness (CP), and shape factor (SF).
